---
title: "Part 2"
author: "Felipe González Arango"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: sandstone
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: yes
---

## Part Two: Data Analysis (150 points)

**Create a new R Markdown file for Part Two.**

Make sure your final file is carefully formatted, so that each analysis is clear and concise.  
Be sure your knitted .html file shows all your source code.


### The Data

Use the dataset `Oscars-demographics-DFE.csv` in this repository.

To accomplish the tasks in this exam, you will need to do appropriate cleaning, adjusting, and reorganizing of the data.

In what follows, the phrase "Big 5 Awards" refers to the five individual Academy Awards covered in this dataset:  
Best Director, Best Actor, Best Actress, Best Supporting Actor, and Best Supporting Actress.

### Warm-ups (10 points each)

1. Which movie(s) won the most unique "Big 5" awards?

```{r message=FALSE, warning=FALSE}
library(readr)
library(tidyverse)
library(janitor)
library(vtable)
#Import data base

movies_data <- read_csv("Oscars-demographics-DFE.csv")
movies_data <- clean_names(movies_data) #Clean variable names
st(movies_data)

big_5 <- c("Best Actor", "Best Director", "Best Actress", "Best Supporting Actor","Best Supporting Actress") #Creat vector for Big 5

movies_data %>% 
  group_by(movie) %>% 
  distinct(award) %>% 
  count() %>% 
  arrange(desc(n))



```


2. Of all actresses who have won the Best Actress award, what are is the most common first name?  

```{r}
library(unglue)
library(magrittr)

movies_data %>% 
  filter(award=="Best Actress") %>% 
  select(person) %>% 
  distinct(person) %>% 
  unglue_unnest(., person,"{FirstName} {LastName}") %$%  # This makes two columns one with the fisrt name and the other with the last name
  table(FirstName)
```

The name is Helen. 

3. What US State, or non-US country, has produced the most Oscar winners (for the awards in this dataset)?

```{r}
freq <-  sub('.*,\\s*', '', movies_data$birthplace)
freq[freq[]=="Ny"] <- "New York City" #Changes all values of Ny for the long one

freq <- table(freq)#Creates a frequency table of the States or countries

which.max(freq) #Gives the value
```


### Age and Gender (60 points)

The information in this dataset includes two awards given only to women (Best Actress, Best Supporting Actress) 
and two awards given only to men (Best Actor, Best Supporting Actor).  

Create a linear model that explores how the typical age of acting award winners has changed over time, 
and how that effect is different for the two genders of awards.

*(Note:  You will absolutely need to do some careful manipulation of the date information in this dataset, before you create your model.
You may assume all Oscar awards take place on Feb 1 of the year they are awarded.)*

Print out the results of your model, and briefly discuss the interpretations and conclusions.


### Bootstrapping (60 points)

Use a bootstrap approach to answer the following question:  
What is an approximate 95% confidence interval for percent of "Big 5 Award" award winners who are not white?

In addition to the confidence interval, make a plot that illustrates your findings.
